Graph Exploration and Search

### 2017-11-13 paper.tex
Fixed a definition

\title*{Graph Exploration and Search}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{Yinghui Wu\\Davide Mottin}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{Yinghui Wu, Washington State University, \email{yinghui@eecs.wsu.edu}}
%
\institute{Hasso Plattner Institute, \email{davide.mottin@hpi.de}}
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

@@

\stitle{Refinement of Graph Query Results} is needed to deal with the overwhelming amount of results that is typical in subgraph processing. It includes approaches designed to present comprehensive result sets to the user or intermediate results that can be refined further. Instantiations of this kind are graph summaries, top-k methods, query reformulation, and skyline queries. 
	% \item [Focused Graph Mining] guides the users to a specific portion of the graph they are interested in. It requires the user to provide feedback in the process to restrict the computation to some portion of the graph. Ego-networks mining belongs to this strategy, since the user search is limited to a particular area of the graph and the algorithms focus on that specific area.

>>>>

\title*{Graph Exploration and Search}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{Davide Mottin\\ Yinghui Wu}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
%
\institute{Davide Mottin， Hasso Plattner Institute, \email{davide.mottin@hpi.de}\\ 
Yinghui Wu, Washington State University, \email{yinghui@eecs.wsu.edu}}
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

@@

\stitle{Refinement of Graph Query Results} is needed to deal with the overwhelming amount of results that is typical in subgraph processing. It includes approaches designed to present comprehensive result sets to the user or intermediate results that can be refined further. 
%Instantiations of this kind are graph summaries, top-k methods, query reformulation, and skyline queries. 
	% \item [Focused Graph Mining] guides the users to a specific portion of the graph they are interested in. It requires the user to provide feedback in the process to restrict the computation to some portion of the graph. Ego-networks mining belongs to this strategy, since the user search is limited to a particular area of the graph and the algorithms focus on that specific area.
